Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-01-31 paper/experiments.tex
Update
Paper update

@@

\begin{enumerate}
        \item Hart6
        \item Alpine1
        \item Branin
        \item Rosenbrock-2
        \item Rosenbrock-10
        \item Ackley-2
        \item Ackley-10
\end{enumerate}

@@

\begin{figure}[]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{./img/mean_DAC2014.eps}}
\caption{Optimization results of the operational amplifier}
\label{resDAC2014}
\end{center}
\vskip -0.2in
\end{figure}

>>>>

% TODO: more details about the setup of experiments

We compared the proposed MACE algorithm with several state-of-the-art parallel Bayesian optimization methods, including the BLCB algorithm\footnote{We implemented this algorithm, as the available open source implementation only takes discrete input}, the local penalization method with EI acquisition function\footnote{Code downloade from https://github.com/SheffieldML/GPyOpt}, the qKG and qEI method\footnote{The code for qKG and qEI is available at https://github.com/wujian16/Cornell-MOE}. The MACE algorithm and the BLCB algorithm are implemented using c++ language.

@@

We tested the MACE algorithm and other parallel BO method using seven benchmark
functions, including the branin function, the alpine1 function, the 6D hartmann
function, the 2D and 10D ackley function and the 2D and 10D Rosenbrock
function. The dimensions and design space are summarized in Table~ref{tab:summaryanalygical}.

% \begin{table}[htbp]
%     \small
%     \centering
%     \caption{Summary of the analytical benchmark functions}
%     \label{tab:summaryanalygical}
%     \begin{tabular}
%         \toprule
%         Function     & Dimension    & SearchDomain         \\ 
%         \midrule
%         Branin       & 2            & $[-5, 10]\times[0, 15]$ \\
%         Alpine1      & 5            & $[-10, 10]^5$           \\
%         Hartmann6    & 6            & $[0, 1]^6$              \\
%         Ackley2      & 2            & $[-32, 32]^2$           \\
%         Ackley10     & 10           & $[-32, 32]^10$          \\
%         Rosenbrock2  & 2            & $[-5, 10]^2$            \\
%         Rosenbrock10 & 10           & $[-20, 20]^10$          \\
%         \bottomrule
%     \end{tabular}
% \end{table}

\begin{table}[htbp]
    \centering
    \caption{Summary of the analytical benchmark functions}
    \label{tab:summaryanalygical}
    \begin{tabular}{llllllll}
        \toprule
        Function            & Dimension        & Search domain    \\ \midrule
         Branin             & 2                & $[-5, 10]\times[0, 15]$ \\
         Alpine1            & 5                & $[-10, 10]^5$           \\
         Hartmann6          & 6                & $[0, 1]^6$              \\
         Ackley2            & 2                & $[-32, 32]^2$           \\
         Ackley10           & 10               & $[-32, 32]^{10}$          \\
         Rosenbrock2        & 2                & $[-5, 10]^2$            \\
         Rosenbrock10       & 10               & $[-20, 20]^{10}$          \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{enumerate}
        \item Branin
        \item Alpine1
        \item Hart6
        \item Rosenbrock-2
        \item Rosenbrock-10
        \item Ackley-2
        \item Ackley-10
\end{enumerate}

@@

\begin{figure}[htbp]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{./img/mean_DAC2014.eps}}
\caption{Optimization results of the operational amplifier}
\label{resDAC2014}
\end{center}
\vskip -0.2in
\end{figure}

\subsection{ClassE Power Amplifier}

\begin{figure}[htbp]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{./img/ClassE_mean.eps}}
\caption{Optimization results of the class-E power amplifier}
\label{resDAC2014}
\end{center}
\vskip -0.2in
\end{figure}

### 2018-01-31 paper/mace.tex
Paper update

We propose a novel heuristic for the parallelization of Bayesian optimization.
The parallelization is realized via multi-objective ensemble of multiple
acquisition functions. When we have multiple acquisition functions built from
the same GP model, they may not disagree with each other about which point is
most promising, for example, the value of LCB function always decreases as the
$\sigma(\bm{x})$ increases, however, for the PI function, when $\sigma{\bm{x}}$
increases, the value of PI would decrease when $\mu(\bm{x}) < \tau$, and
increase when $\mu(\bm{x}) > \tau$.

@@

With multi-objective optimization, the disagreement between different
acquisition function can be used for the parallelization of Bayesian
optimization. In the standard Bayesian optimization, one acquisition function
is specified, and in each iteration, the single-objective optimization is
performed to optimize the acquisition function; in our proposed MACE algorithm,
multiple acquisition function is pre-specified by the user, in each iteration,
the DEMO multi-objective optimization algorithm is applied to find the Pareto
front of the acquisition functions. Once the Pareto front is obtained, we can
then sample from the Pareto front, and then evaluate these sampled points in
parallel.

@@

We select the LCB, EI and PI acquisition function in our implementation of the MACE algorithm, but other acquisition functions like KG and PES can also be incorporated into the MACE framework. The proposed MACE algorithm is described in Algorithm~\ref{alg:MACE}.

\begin{algorithm}
\caption{Multi-objective Acquisition Ensemble Algorithm}
\label{alg:MACE}
\begin{algorithmic}[1]
\STATE Initial Sampling
\STATE Construct initial GP model
\FOR{t = 1, 2, \dots}
    \STATE Construct the LCB, EI and PI function according to \eqref{eq:LCB} and \eqref{eq:PI_EI}
    \STATE Find the Pareto front of LCB, EI, PI function using the DEMO algorithm
    \STATE Randomly sample B points $\bm{x}_1, \dots, \bm{x}_B$ from the Pareto front
    \STATE Evaluate $\bm{x}_1, \dots, \bm{x}_B$ to get $y_1 = f(\bm{x}_1),~\dots~,y_B = f(\bm{x}_B)$
    \STATE Update the GP model
\ENDFOR
\STATE Return best $f(\bm{x})$ recorded during iterations
\end{algorithmic}
\end{algorithm}

>>>>

We propose a novel heuristic for the parallelization of Bayesian optimization.
The parallelization is realized via multi-objective ensemble of multiple
acquisition functions. When we have multiple acquisition functions built from
the same GP model, they may not disagree with each other about which point is
most promising. For example, the value of LCB function always decreases as the
$\sigma(\bm{x})$ increases, however, for the PI function, when $\sigma(\bm{x})$
increases, the value of PI would decrease when $\mu(\bm{x}) < \tau$, and
increase when $\mu(\bm{x}) > \tau$.

@@

With multi-objective optimization, the disagreement between different
acquisition function can be used for the parallelization of Bayesian
optimization, as best trade-off between these acquisition functions can be
captured by the Pareto front.

In the proposed MACE algorithm, the LCB, EI, and PI acquisition functions are selected, but other acquisition functions like KG and PES can also be incorporated into the MACE framework. In each iteration, the following MO problem is constructed:
\begin{equation}
    \label{eq:MO_LCB_EI_PI}
    \begin{aligned}
        & \text{minimize} & & \mathrm{LCB}(\bm{x}),~-\mathrm{EI}(\bm{x}),~-\mathrm{PI}(\bm{x}).
    \end{aligned}
\end{equation}
Then the DEMO multi-objective optimization algorithm is applied to solve \eqref{eq:MO_LCB_EI_PI}. Once the Pareto front of LCB, EI and PI is obtained, the candidate evalution points are then randomly sampled from the Pareto front.

@@

The proposed MACE algorithm is described in Algorithm~\ref{alg:MACE}.

\begin{algorithm}
\caption{Multi-objective Acquisition Ensemble Algorithm}
\label{alg:MACE}
\begin{algorithmic}[1]
\STATE Initial Sampling
\STATE Construct initial GP model
\FOR{t = 1, 2, \dots}
    \STATE Construct the LCB, EI and PI functions according to \eqref{eq:LCB} and \eqref{eq:PI_EI}
    \STATE Find the Pareto front of LCB, EI, PI function using the DEMO algorithm
    \STATE Randomly sample B points $\bm{x}_1, \dots, \bm{x}_B$ from the Pareto front where B is the batch size
    \STATE Evaluate $\bm{x}_1, \dots, \bm{x}_B$ to get $y_1 = f(\bm{x}_1),~\dots~,y_B = f(\bm{x}_B)$
    \STATE Update the GP model
\ENDFOR
\STATE Return best $f(\bm{x})$ recorded during iterations
\end{algorithmic}
\end{algorithm}
